A Gaussian process model of human electrocorticographic data

### 2020-02-15 paper/main.tex
working on information maps section

We also wondered whether the map of information scores might vary as a function of the spectral
components of the activity patterns under consideration.  For example, low frequency $\delta$ activity in the thalamus has been implicated in
supporting connectivity with cortex~\citep[e.g.,][]{Jone09}; $\theta$ activity
in frontal regions have been implicated in memory consolidation~\citep{NishEtal09} and integration~\citep{BackEtal16}; parietal and occipital $\alpha activity has been
implicated in attention modulation~\citep[e.g., see][]{Klim12}; $\beta$ activity in motor cortex have been implicated in motor control and processing~\citep{BrovEtal04, KoelEtal08, RubiEtal06};
and occipital $\gamma$ activity has been implicated in visual attention and visual processing~\citep{ZhouEtal16, TallEtal05, FrieEtal07}.
We computed analogous maps of information scores for each individual frequency band.  Across Datasets 1 and 2 we observed a weak, but statistically reliable, correspondence in
these maps, aside from in the $\alpha$ band ($\delta$: $r = 0.09, p < 10^{-57}$; $\theta$: $r = 0.24, p < 10^{-60}$; $\alpha$: $r = -0.03, p < 0.001$, $\beta$: $r = 0.02, p - 0.0011$; $\gamma_L$: $r = 0.1, p < 10^{-67}$; $\gamma_H$: $r = 0.03, p < 10^{-7}$; broadband: $r = 0.21, p < 10^{-297}).

%%%% STOPPED HERE...

>>>>

We also wondered whether the map of information scores might vary as a function of the spectral
components of the activity patterns under consideration.  For example, low frequency $\delta$ activity in the thalamus has been implicated in
supporting connectivity with cortex~\citep[e.g.,][]{Jone09}; $\theta$ activity
in frontal regions have been implicated in memory consolidation~\citep{NishEtal09} and integration~\citep{BackEtal16}; parietal and occipital $\alpha activity has been
implicated in attention modulation~\citep[e.g., see][]{Klim12}; $\beta$ activity in motor cortex have been implicated in motor control and processing~\citep{BrovEtal04, KoelEtal08, RubiEtal06};
and occipital $\gamma$ activity has been implicated in visual attention and visual processing~\citep{ZhouEtal16, TallEtal05, FrieEtal07}.
We computed analogous maps of information scores for each individual frequency band.  Across Datasets 1 and 2 (with the exception of $\alpha$ band activity), we observed reliable positive correlations
between the voxel-by-voxel maps of information scores ($\delta$: $r = 0.09, p < 10^{-57}$; $\theta$: $r = 0.24, p < 10^{-60}$; $\alpha$: $r = -0.03, p < 0.001$, $\beta$: $r = 0.02, p - 0.0011$; $\gamma_L$: $r = 0.1, p < 10^{-67}$; $\gamma_H$: $r = 0.03, p < 10^{-7}$; broadband: $r = 0.21, p < 10^{-297}).

%%%%STOPPED HERE
